






```{r}
#Reading our data

##Since we have already imported our dataset, we will preview the first 6 rows of the data.

head(advertising)

```




```{r}
##Previewing the bottom of our dataset

tail(advertising)


```

```{r}
##Determining the number of records in our data

dim(advertising)


```

```{r}
## Previewing the column names in our data

colnames(advertising)

```
```{r}
##Obtaining a summary of our data

summary(advertising)


```
```{r}
#Tidying our dataset

## Checking for any duplicated values

Duplicate <- advertising[duplicated(advertising),]

Duplicate

## We have confirmed that our data has no duplicated values.
```

```{r}
## Checking for any missing values

colSums(is.na(advertising))

## Our data has no missing values, hence ready for analysis
```

```{r}
## Assigning our numerical columns to their variable names

age <- advertising$Age
area <- advertising$`Area Income`
time <- advertising$`Daily Time Spent on Site`
usage <- advertising$`Daily Internet Usage`


```



```{r}
## Plotting boxplots to visualize outliers in our numerical columns

boxplot(age)
```


```{r}
## Visualisation of outliers in the Area income column

boxplot(area)

## This column happens to be the only column with outliers

```


```{r}
## A boxplot visual of Daily Time Spent on Site

boxplot(time)
```


```{r}
##A visual for Daily Internet Usage

boxplot(usage)
```


```{r}
## Showing the outliers in our Area Income column

boxplot.stats(area)$out

## All our outliers are income values less than 20,000
```


```{r}
## Dropping the outliers in our data

data <- subset(advertising,`Area Income` > 19000)

data
```


```{r}
## Dtermining the classes available in our data
class(data)
```


```{r}
#Univariate Analysis

## Determining the mean on our Area Income column

area_mean <- mean(data$`Area Income`)


area_mean
```

```{r}
## Calculating the mean of Daily Time Spent on Site

time_mean <- mean(data$`Daily Time Spent on Site`)

time_mean
```

```{r}
## Calculating the median of Area Income

area_median <- median(data$`Area Income`)

area_median

```


```{r}
## Calculating the mean of Ages
age_mean <- mean(data$Age)

age_mean
```

```{r}
## Determining the median of our Age column

age_median <- median(data$Age)

age_median

```

```{r}
## Creating getmode function to determine the modes of our columns

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

```




```{r}
## Determining the mode of Age

age_mode <- getmode(age)

age_mode
```

```{r}
## Calculating the mode of income

area_mode <- getmode(area)

area_mode
```
```{r}
## Determining the mode of daily time spent on the site

time_mode <- getmode(time)

time_mode
```


```{r}
# Calculating the quantiles in our numeric columns

age_quantile <- quantile(data$Age)


age_quantile
```

```{r}

time_quantile <- quantile(data$`Daily Time Spent on Site`)

time_quantile
```




```{r}
area_quantile <- quantile(data$`Area Income`)

area_quantile

```

```{r}
## Calculating the variance for our columns
### Age 

age_var <- var(data$Age)

age_var

```

```{r}
### Daily Time Spent On Site

time_var <- var(data$`Daily Time Spent on Site`)

time_var
```

```{r}
## Calculating the range in the Age column

age_range <- range(data$Age)

age_range

```

```{r}
## Plotting a barplot for our age column.
age <- data$Age

age_ref <- table(age)

barplot(age_ref)

## People between the age of 28 and 37 consist of the highest number of of people who visit the site on average.
```

```{r}
# Bivariate analysis

## Calculating the correlation between our age and daily time columns

cor(age, time)

## These show a weak negative correlation
```
```{r}
## Correlation between male and age columns

male <- data$Male

cor(male, age)

### This also show weak negative correlation
```
```{r}
## Covariance between age and daily time spent on site

cov(age, time)

## There is strong negative covariance, which shows that they behave opposite to each other.

``````

`````{r}

## Plotting a scatterplot representing our age and time columns.

plot(age, time, xlab = "Age", ylab = "Daily Time Spent On Site")

```


### We have concluded that individuals between the age of 28 and 36 years spend the most time on the site.
### Average income from individuals that mostly use the site is around 57,000 which means the entreprenuer should aim for high income individuals while advertising.
### The average time spent on the site is around 62 minutes, hence she can know the length of her advertisements.
